### 2021-07-15 src/paper/data/school_policies.tex
Typos etc in validation exercise and some improvements to the references trying to resolve error.

@@

% school
Until November schools were open normally. Starting in November, we assume that increased
hygiene measures were taken or that hygiene measures were more carefully observed as the
incidence increased. Schools stayed open until mid December.
% mid Dec until mid Jan
From mid December until January 10 schools closed only offered so called ``emergency
care'' for young children whose parents could credibly demonstrate that both had to work
and had no other child care arrangement. Approximately 25\% of primary students and 5\%
of secondary students attended school as a result.
% Jan and Feb
After January 10 when parents had returned to work the rules for emergency care were
relaxed and we assume a third of primary children and 10\% of secondary students attended
school as a result. In addition, graduating classes (most adolescents between 16 and 18)
were allowed to return to school in a rotating scheme where each class was split in two
groups. Relying on anecdotal evidence we assume that the groups rotate on a daily basis.
% mid Feb to mid March
Starting on February 22 primary students were also allowed to return to school on a
rotating basis until mid March.
% mid March to Easter
We summarize the school policy from mid March until Easter as all students being on a
rotating school schedule. In addition, children that qualify for emergency care also
attend on days where there group is scheduled to not attend school physically
% after Easter
After the Easter break schools were mostly closed again. Part of this was a federal law,
the so called ``Bundesnotbremse'' \citep{Notbremse2021} that set some binding rules for
schools based on local incidences that were binding at the time. As a result, most states
adjusted there schooling policies and during April most schools were closed with
emergency care arrangements as in the time from January 10 to February 21. As cases fell
schools were allowed to gradually open. We summarize this as students being on the same
rotating schedule as from mid March to Easter starting on May 1 \citep{school_BW,
school_BWa, school_BWb , school_BY, school_BYa, school_NRW, school_NRWa, school_NRWb,
school_NRWc}.

% young educ
The policies for preschools and nurseries are similar to the school policies but simpler.
Until November children attended completely normally, starting in November with increased
hygiene measures. Nurseries and preschools stayed open until mid December. From mid
December until January 10, nurseries and preschools were nearly completely closed. If
parents could credibly demonstrate that both parents work in systemically relevant
professions and no other child care arrangement was possible, nurseries and preschools
offered so called ``emergency care''. We assume 10\% of children qualified and used
emergency care during this time. After January 10 when parents had returned to work the
rules for emergency care were relaxed and we assume a third of children attended nursery
and preschool. This policy stayed in place until February 20. Afterwards, preschools and
nurseries were open normally (still with increased hygiene measures) until mid March.
Then during the third wave the restrictions February were put back into place until end
of April when nurseries and preschools opened again and stayed open for the rest of our
simulation period with increased hygiene measures in place. \citep{KiTa_BY, KiTa_NRW,
KiTa_BW, KiTa_BWa, KiTa_BYa, school_BWb}.

>>>>

 \comment[id=K]{@Janos: Read this!}

@@

% school
Until November schools were open normally. Starting in November, we assume that increased
hygiene measures were taken or that hygiene measures were more carefully observed as the
incidence increased. Schools stayed open until mid December.
% mid Dec until mid Jan
From mid December until January 10 schools closed only offered so called ``emergency
care'' for young children whose parents could credibly demonstrate that both had to work
and had no other child care arrangement. Approximately 25\% of primary students and 5\%
of secondary students attended school as a result.
% Jan and Feb
After January 10 when parents had returned to work the rules for emergency care were
relaxed and we assume a third of primary children and 10\% of secondary students attended
school as a result. In addition, graduating classes (most adolescents between 16 and 18)
were allowed to return to school in a rotating scheme where each class was split in two
groups. Relying on anecdotal evidence we assume that the groups rotate on a daily basis.
% mid Feb to mid March
Starting on February 22 primary students were also allowed to return to school on a
rotating basis until mid March.
% mid March to Easter
We summarize the school policy from mid March until Easter as all students being on a
rotating school schedule. In addition, children that qualify for emergency care also
attend on days where there group is scheduled to not attend school physically
% after Easter
After the Easter break schools were mostly closed again. Part of this was a federal law,
the so called ``Bundesnotbremse'' \citep{Notbremse2021} that set some binding rules for
schools based on local incidences that were binding at the time. As a result, most states
adjusted there schooling policies and during April most schools were closed with
emergency care arrangements as in the time from January 10 to February 21. As cases fell
schools were allowed to gradually open. We summarize this as students being on the same
rotating schedule as from mid March to Easter starting on May 1 \citep{schoolBW,
schoolBWa, schoolBWb, schoolBY, schoolBYa, schoolNRW, schoolNRWa, schoolNRWb,
schoolNRWc}.

% young educ
The policies for preschools and nurseries are similar to the school policies but simpler.
Until November children attended completely normally, starting in November with increased
hygiene measures. Nurseries and preschools stayed open until mid December. From mid
December until January 10, nurseries and preschools were nearly completely closed. If
parents could credibly demonstrate that both parents work in systemically relevant
professions and no other child care arrangement was possible, nurseries and preschools
offered so called ``emergency care''. We assume 10\% of children qualified and used
emergency care during this time. After January 10 when parents had returned to work the
rules for emergency care were relaxed and we assume a third of children attended nursery
and preschool. This policy stayed in place until February 20. Afterwards, preschools and
nurseries were open normally (still with increased hygiene measures) until mid March.
Then during the third wave the restrictions February were put back into place until end
of April when nurseries and preschools opened again and stayed open for the rest of our
simulation period with increased hygiene measures in place. \citep{KiTa_BY, KiTa_NRW,
KiTa_BW, KiTa_BWa, KiTa_BYa, schoolBWb}.

### 2021-07-15 src/paper/results/validation.tex
Typos etc in validation exercise and some improvements to the references trying to resolve error.

Achieving a good in-sample fit does not necessarily guarantee that our model will also be
able to make out of sample predictions. For example, it could be that the results are
very sensitive to the exact number of vaccinations, the work mobility multiplier
($\rho_{w,\:attend,\:t}$) or the number of rapid tests (governed by the $\pi$ parameters)
that are performed -- all of which are things that cannot be known exactly ex-ante.

@@

\begin{figure}[ht] % Robustness Check
  \centering
  \begin{subfigure}[b]{.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/robustness_check/full_new_known_case}
    \caption{Reported Cases}
    \label{fig:robustness_check_new_known_case}
  \end{subfigure}%
  \hfill
  \begin{subfigure}[b]{.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/robustness_check/full_newly_infected}
    \caption{Total Cases}
    \label{fig:robustness_check_newly_infected}
  \end{subfigure}
  \caption{Out of Sample Prediction for Reported and Total Cases from March to June
  2021.}
  \label{fig:robustness_check_detailed}
  \floatfoot{\noindent \textit{Note:} The ex-post scenario is an in-sample prediction
  that uses all available information and is very close to actual case numbers. For the
  other scenarios data on vaccinations, work mobility and rapid tests that became
  available after March 1 have been replaced by prediction models that are calibrated
  with data from February. Moreover, they do not model a lower number of detected cases
  over the Easter holidays. The different scenarios make different assumptions on the
  date at which full availability of rapid tests is reached. While the out of sample
  predictions differ substantially for the exact case numbers at the beginning of June
  (between 20 and 70 cases per million), they can all reproduce the decline in case
  numbers that is jointly driven by seasonality, large scale rapid tests and
  vaccinations. For legibility reasons, all lines are rolling 7-day averages.}
\end{figure}

>>>>

Achieving a good in-sample fit does not necessarily guarantee that our model will also be
able to make out of sample predictions. For example, it could be that the results are
very sensitive to the exact number of vaccinations, the work mobility multiplier
($\rho_{w,\:attend,\:t}$) or the number of performed rapid tests (governed by the $\pi$
parameters) -- all of which are things that cannot be known exactly ex-ante.

@@

\begin{figure}[ht] % Robustness Check
  \centering
  \begin{subfigure}[b]{.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/robustness_check/full_new_known_case}
    \caption{Reported Cases}
    \label{fig:robustness_check_new_known_case}
  \end{subfigure}%
  \hfill
  \begin{subfigure}[b]{.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/robustness_check/full_newly_infected}
    \caption{Total Cases}
    \label{fig:robustness_check_newly_infected}
  \end{subfigure}
  \caption{Out of Sample Prediction for Reported and Total Cases from March to June
  2021.}
  \label{fig:robustness_check_detailed}
  \floatfoot{\noindent \textit{Note:} The ex-post scenario is an in-sample prediction
  that uses all available information and is very close to actual case numbers. For the
  other scenarios data on vaccinations, work mobility and rapid tests that became
  available after March 1 have been replaced by prediction models that are calibrated
  with data from February. Moreover, they do not model a lower number of detected cases
  over the Easter holidays. The different scenarios make different assumptions on the
  date at which full availability of rapid tests is reached. While the out of sample
  predictions differ substantially for the exact case numbers at the beginning of June
  (between 20 and 70 cases per million), they can all reproduce the decline in case
  numbers that is jointly driven by seasonality, large scale rapid tests and
  vaccinations. For legibility reasons, all lines are rolling 7-day averages. Each line
  is the average over 30 simulation runs.}
\end{figure}

Another form of validating our model is to see how well our main results align with
other studies that evaluate the effect of large scale rapid testing. Of course, this
has to be taken with a grain of salt as the effect of any rapid testing policy depends
on the incidence of the disease in the population, how well other testing policies
such as PCR tests are working, the effect of seasonality and NPIs that are in place.

Nevertheless, it is reassuring that other studies find effect sizes in the same order
of magnitude.

\citet{Pavelka2021} estimate that a mass testing campaign in Slovakia in October and
November 2020 where approximately 65 \% of the population took a rapid test within a two
week period lead to a reduction in case numbers of 70 \% three weeks after the start
of the intervention. Moreover, they find that this strong reduction in
cases cannot be explained by isolation of people who tested positive alone but only when
they took into account that household members of people who tested positive reduced
their contacts.

While we do not model the exact scenario of \citet{Pavelka2021}, we can roughly compare
their estimates with our predictions for the difference between the baseline scenario
and and a scenario without rapid tests. In May about 45\% of people do
at least one rapid test in every week. Taking into account that there are many repeated
testers the number of people who do a test within a two week period is probably
slightly less than the 65\% from the intervention in Slovakia. On the other hand, we
have many people who do more than one rapid test in that time which also leads to the
detection of cases. Our model predicts that the observed incidence with tests is
approximately 65\% lower than without tests after three weeks.
Thus we have an effect size in the same order of magnitude but are slightly
less optimistic regarding the efficiency of rapid tests.

\citet{Berger2021} analyse the effect of twice weekly rapid testing in schools. They
have two main findings: Firstly, rapid tests reduced the share of undetected cases
among students by a factor between two and four. Secondly, open schools with mandatory
testing might lead to the same or even lower numbers of infections than closed
schools. The estimates are based on infection numbers after the Easter holiday.

Again, we do not directly simulate their scenarios but can roughly compare our results
to theirs. We estimate a share of undetected cases of approximately 75\% among school
age children (five to 14 years) at the beginning of April, see
Figure~\ref{fig:share_known_cases_by_age_group}. This drops to slightly less than 40\%
at the end of our simulation period. Thus in the long run, mandatory tests at schools
led to a reduction of the share of undetected cases by a factor of more than 1.8 which
is just slightly below the factor of two to four predicted by \citet{Berger2021}.

Similarly we are slightly less optimistic for the effect of opening schools with testing
compared to closing schools. While they predict that opening schools could even be
beneficial we estimate that it would lead to a slight increase in case numbers see
Figure~\ref{fig:school_scenarios_detailed}).

% In May 45 % per week are tested
% Incidence pessimistic = 1750
% Incidence with mass testing = 750
